Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-06-06 paper.qmd
Mostly preparing plots for the stage 2 confirmatory study

```{r}
source('functions.R')
source('pilot_analysis.R')
source('simulate.R')
source('sexspecificmodels.R')
source('stage2_analysis.R')
```

@@

```{r}
#| label: fig-coefs
#| fig-width: 10
#| fig-height: 8
#| fig-cap: Coefficients of sex-specific strength, and strength X sex interaction for our four mating success outcomes and our five sets of potential confounding variables. Partnered coefficients are from logistic regressions, partner number coefficients are from quasi-Poisson glm regressions, and age at first sex coefficients are from Gaussian glm regressions. Bars are 95\% CIs. For the full regression tables, see the SI.

plot_coefs
```

@@

# Confirmatory Study (Not yet conducted)

@@

@@

### Effects plots

@@

Effects of sex-specific standardized strength on mating outcomes, by sex. Strength is centered and scaled by 2 SD, separately for each sex. Plots are based on the anthropometric control models, with control variables held at their mean values.
:::

@@

@@

>>>>

```{r}
source('functions.R')
source('pilot_analysis.R')
source('simulate.R')
source('sexspecificmodels.R')
source('stage2_analysis.R')
source('compare.R')
```

@@

```{r}
#| label: fig-coefs
#| fig-width: 10
#| fig-height: 8
#| fig-cap: Coefficients of sex-specific strength, and strength X sex interaction for our four mating success outcomes and our five sets of potential confounding variables. Partnered coefficients are from logistic regressions, partner number coefficients are from quasi-Poisson glm regressions, and age at first sex coefficients are from Gaussian glm regressions. Bars are 95\% CIs. Left: Pilot study results. Right: Confirmatory study results. For the full regression tables, see the SI.

plot_coefs + plot_coefs_stage2 + plot_layout(axes = 'collect_y', axis_titles = 'collect')
```

@@

# Stage 2 Confirmatory Study

@@

## Deviation from Stage 1 method

Models and R code for three of our four mating success outcome variables remain identical to those used in the Stage 1 pilot study. However, although the Poisson regression model of lifetime sexual partners in the pilot study included age as a control, it is more appropriate to instead include it as an exposure variable (an offset) in the model, which we now do. We also treat this exposure as years since sexual maturity (age - 12 years). The change in the strength and strength:sex coefficients from this change in model specification is minimal (see @sfig-comparison).

## Results

```{r}
#| label: fig-stage2coef
#| fig-width: 10
#| fig-height: 8
#| fig-cap: Coefficients of sex-specific strength, and strength X sex interaction for our four mating success outcomes and our five sets of potential confounding variables. Partnered coefficients are from logistic regressions, partner number coefficients are from quasi-Poisson glm regressions, and age at first sex coefficients are from Gaussian glm regressions. Bars are 95\% CIs. For the full regression tables, see the SI.

plot_coefs_stage2
```

:::{#fig-stage2effects}
```{r}
effects_plots(models_stage2)
```

Effects of sex-specific standardized strength on mating outcomes, by sex. Strength is centered and scaled by 2 SD, separately for each sex (almost all participants therefore fall between -1 and 1). Plots are based on the anthropometric control models, with control variables held at their mean values. Lifetime partners is modeled as the rate of new partners per year since reaching sexual maturity (age 12).
:::

@@

### Effects plots (Pilot)

@@

Effects of sex-specific standardized strength on mating outcomes, by sex. Strength is centered and scaled by 2 SD, separately for each sex (almost all participants therefore fall between -1 and 1). Plots are based on the anthropometric control models, with control variables held at their mean values. Lifetime partners is modeled as the rate of new partners per year since reaching sexual maturity (age 12).
:::

@@

```{r}
out_sexspecific_pilot <- sex_specific_models(designsG)
plot_sexspecific_strength_coefs <- out_sexspecific_pilot$plot
dfmodelsummaries <- out_sexspecific_pilot$summaries
```

@@

## Stage 2 confirmatory study

:::{#sfig-comparison}
```{r}
plot_compare
```

A comparison of strength and strength:sex cofficients with the original model specification for the lifetime sex partners (anthropometric controls) that included age as a control variable (orignal), and the specification that now instead includes years since sexual maturity (age-12) as an exposure variable (offset) (new). Both models are quasi-Poisson models.
:::
